Defending Against Web Application Attacks: Approaches, Challenges and Implications \newline\newline \small{\textbf{Response to Review Comments}}

### 2016-07-26 docs/comments/comments.tex
some notes on R2's 1st comment

\titlespacing*{\section}
{0pt}{1ex}{0.55ex}
\titlespacing*{\subsection}
{0pt}{1ex}{0.55ex}
\titlespacing*{\subsubsection}
{0pt}{1ex}{0.55ex}

\setlength{\footnotesep}{0.28cm}
\setlength{\skip\footins}{0.1cm}

@@

\noindent
{\bf Comment 3:} ``Some minor comments for the authors:
\begin{enumerate}
\item Introduction: ``didn't" $\rightarrow$ did not
\item Introduction: ``haven't" $\rightarrow$ have not
\item Section 2: PHP Object Injection vulnerabilities do not have to be
 ``part of cookies". These could come any user input, not necessarily
 cookies (similar to other code injection vulnerabilities).
\item Section 4.5 ``canny attacks" and ``cannier attacker" should probably
 be ``savvy" or a different word.
\item Section 5.1.2 it is not clear from your description that the CSP
 policy is communicated via HTTP header. This may not be clear to
 those readers that aren't familiar with CSP.
\item Section 5.1.2 ``XXS" $\rightarrow$ ``XSS".
\item Section 5.2.1 ``maybe" $\rightarrow$ ``may be"".
\end{enumerate}

@@

@@

\noindent
{\bf Comment 3:} ``Some recent works in the (or related) 
ield are not discussed in this paper.
For example, information flow control solutions and
proposals that confine or isolate JavaScript could
be used to defend against code injection attacks.
Examples are: {\sc jsf}low: Tracking information
flow in JavaScript and its {\sc api}s ({\sc sac}'14).
Protecting users by confining JavaScript with {\sc cowl} ({\sc osdi} '14).
Runtime monitoring and formal analysis of information
fows in Chromium ({\sc ndss} '15)."\\

>>>>

@@

\noindent
{\bf Comment 3:} ``Some minor comments for the authors:
\begin{enumerate}
\item Introduction: ``didn't" $\rightarrow$ did not
\item Introduction: ``haven't" $\rightarrow$ have not
\item Section 2: {\sc php} Object Injection vulnerabilities do not have to be
 ``part of cookies". These could come any user input, not necessarily
 cookies (similar to other code injection vulnerabilities).
\item Section 4.5 ``canny attacks" and ``cannier attacker" should probably
 be ``savvy" or a different word.
\item Section 5.1.2 it is not clear from your description that the {\sc csp}
 policy is communicated via {\sc http} header. This may not be clear to
 those readers that aren't familiar with {\sc csp}.
\item Section 5.1.2 ``{\sc xxs}" $\rightarrow$ ``{\sc xss}".
\item Section 5.2.1 ``maybe" $\rightarrow$ ``may be"".
\end{enumerate}

@@

\noindent
{\bf Response:}
Initial note:
This is an interesting comment.
We need to mention that we did not intend to
compare the mechanisms with each other.
Our intention was to highlight that currently there
are many different testing setups and
environments for defenses that counter
similar attacks (see Subsection 6.1).\\

@@

\noindent
{\bf Comment 3:} ``Some recent works in the (or related) 
field are not discussed in this paper.
For example, information flow control solutions and
proposals that confine or isolate JavaScript could
be used to defend against code injection attacks.
Examples are: {\sc jsf}low: Tracking information
flow in JavaScript and its {\sc api}s ({\sc sac}'14).
Protecting users by confining JavaScript with {\sc cowl} ({\sc osdi} '14).
Runtime monitoring and formal analysis of information
fows in Chromium ({\sc ndss} '15)."\\
